---
output: 
html_document:
  theme: lumen
workflowr:
    knit_root_dir: "analysis"
---
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

```{r, include = FALSE, echo = FALSE}
library(here)
library(workflowr)

#Read in functions
source("Size_Limit_Functions.R")

# Read in CSV
species <- read_csv("Final_Species_List.csv")
```

```{r, include = FALSE, echo = FALSE, warning = FALSE, message = FALSE}
### Conduct analysis

## Step 1. Set number of species to analyze
#MyParsList<-apply(species, 1, lh_function)
#saveRDS(MyParsList, file="MyParsList.rds")
MyParsList<-readRDS("MyParsList.rds")

## Step 2. Set SL & FM options 
SL_options<-c(0.9, 1, 1.1, 1.2, 1.3, 1.5, 2)
FM_options<-c(1, 2, 4)

## Step 3. Run analysis function ypr_function
#output<-ypr_function(MyParsList, SL_options, FM_options)
#saveRDS(output, file="output.rds")
output<-readRDS("output.rds")
```

```{r, include = FALSE, echo = FALSE, warning = FALSE, message = FALSE}

## This code creates column formatting that is called when using multi.col=TRUE. Used in positioning two tables/figs side by side
library(stringi)
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
defChunkHook <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- defChunkHook(x, options)
  if(!is.null(options$multi.col)) {
    x    <- gsub("(\n\`\`\`\n##.*?\`\`\`)", "<div>\\1\n</div>", x)  # wrap div around output chunks
    x    <- gsub("(<img.*?>)", "<div>\\1\n</div>", x)               # wrap div around plots
    ncol <- nrow(stri_locate_all(x, regex = "<div.*?>")[[1]])       # get the number of div elements created
    x    <- gsub("<div>", paste0("<div style=\"width:", 100/ncol,"%;\">"), x)  # add the width to the divs
    x    <- paste0("<div class=\"multi-col\" style=\"display: flex; justify-content: space-between; align-items: center;\">\n", x, "</div>")  # wrap the mother div around all of the output
  }
  x
})
```

<div align="center"> <font size="+3"> **Appendix 1** </font> 
<div align="center"> <font size="+2"> Spawning Potential Ratio and Yield per Recruit Analyses </font> 

***

<div align="left"> <font size="+2"> **Acanthuridae - Surgeonfishes** </font> 
  
***
  
```{r, include = FALSE}
src <- lapply(
  c(1:12), 
  FUN = function(x) {
    knitr::knit_expand(
      file = here::here("/child/Species_summary.Rmd"), 
      k = x
    )
  }
)
```
`r knitr::knit(text = unlist(src))`

<div align="left"> <font size="+2"> **Albulidae - Bonefishes** </font> 
  
  ***
  
```{r, include = FALSE}
src <- lapply(
  c(13:14), 
  FUN = function(x) {
    knitr::knit_expand(
      file = here::here("/child/Species_summary.Rmd"), 
      k = x
    )
  }
)
```
`r knitr::knit(text = unlist(src))`


<div align="left"> <font size="+2"> **Carangidae - Jacks** </font>  
  
  ***
  
```{r, include = FALSE}
src <- lapply(
  c(15:21), 
  FUN = function(x) {
    knitr::knit_expand(
      file = here::here("/child/Species_summary.Rmd"), 
      k = x
    )
  }
)
```
`r knitr::knit(text = unlist(src))`

<div align="left"> <font size="+2"> **Holocentridae - Squirrelfishes** </font> 
  
  ***
  
```{r, include = FALSE}
src <- lapply(
  c(22), 
  FUN = function(x) {
    knitr::knit_expand(
      file = here::here("/child/Species_summary.Rmd"), 
      k = x
    )
  }
)
```
`r knitr::knit(text = unlist(src))`

<div align="left"> <font size="+2"> **Lutjanidae - Snappers** </font> 
  
  ***
  
```{r, include = FALSE}
src <- lapply(
  c(23:24), 
  FUN = function(x) {
    knitr::knit_expand(
      file = here::here("/child/Species_summary.Rmd"), 
      k = x
    )
  }
)
```
`r knitr::knit(text = unlist(src))`

<div align="left"> <font size="+2"> **Mugilidae - Mullets** </font> 
  
  ***
  
```{r, include = FALSE}
src <- lapply(
  c(25), 
  FUN = function(x) {
    knitr::knit_expand(
      file = here::here("/child/Species_summary.Rmd"), 
      k = x
    )
  }
)
```
`r knitr::knit(text = unlist(src))`

<div align="left"> <font size="+2"> **Mullidae - Goatfishes** </font> 
  
  ***
  
```{r, include = FALSE}
src <- lapply(
  c(26:29), 
  FUN = function(x) {
    knitr::knit_expand(
      file = here::here("/child/Species_summary.Rmd"), 
      k = x
    )
  }
)
```
`r knitr::knit(text = unlist(src))`

<div align="left"> <font size="+2"> **Scaridae - Parrotfishes** </font> 
  
  ***
  
```{r, include = FALSE}
src <- lapply(
  c(30:34), 
  FUN = function(x) {
    knitr::knit_expand(
      file = here::here("/child/Species_summary.Rmd"), 
      k = x
    )
  }
)
```
`r knitr::knit(text = unlist(src))`

<div align="left"> <font size="+2"> **Serranidae - Sea basses** </font>  
  
  ***
  
```{r, include = FALSE}
src <- lapply(
  c(35), 
  FUN = function(x) {
    knitr::knit_expand(
      file = here::here("/child/Species_summary.Rmd"), 
      k = x
    )
  }
)
```
`r knitr::knit(text = unlist(src))`

<div align="left"> <font size="+2"> **Sphyraenidae - Barracudas** </font>  
  
  ***
  
```{r, include = FALSE}
src <- lapply(
  c(36), 
  FUN = function(x) {
    knitr::knit_expand(
      file = here::here("/child/Species_summary.Rmd"), 
      k = x
    )
  }
)
```
`r knitr::knit(text = unlist(src))`